Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
Edited weak scaling discussion.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@110 36274a68-8941-4c93-80ef-affaed5139da

\begin{figure}[h!]
\centering
\subfigure[Global stiffness assembly]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingAssembly.pdf}
}
\subfigure[Local stiffness computation]{
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
}
\caption{Weak scaling results for computation of local stiffness matrices and global stiffness matrix assembly.  For each run, both the number of MPI nodes and number of elements are increased by a factor of four.}
\end{figure}

Both localized and non-localized local stiffness computation display weak scalability by maintaining a constant runtime as both the problem size and number of processors are increased.  Unlike the localized case, non-localized assembly of the global stiffness matrix does not scale weakly. It's worth noting, however, that though communication costs grow much faster with a poor partitioning of the mesh, the maximum amount of time spent on assembly is still only a fraction of the time spent on computation of local stiffness matrices.

>>>>

\begin{figure}[h!]
\centering
\subfigure[Local stiffness computation]{
\label{fig:weakScalingStiffness}
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingLocal.pdf}
}
\subfigure[Global stiffness assembly]{
\label{fig:weakScalingAssembly}
\includegraphics[scale = \twoFig]{figs/scalingFigs/weakScalingAssembly.pdf}
}
\caption{Weak scaling results for computation of local stiffness matrices and global stiffness matrix assembly.  For each run, both the number of MPI nodes and number of elements are increased by a factor of four.}
\end{figure}

The local stiffness computation for both partition types maintain a constant runtime as the problem size and number of processors increase---that is, both achieve weak scalability for this part of the computation, as can be seen in Figure \ref{fig:weakScalingStiffness}.  Assembly of the global stiffness matrix achieves weak scalability only for the contiguous case, as can be seen in Figure \ref{fig:weakScalingAssembly}. It's worth noting, however, that though communication costs grow much faster with a poor partitioning of the mesh, the maximum amount of time spent on assembly is still only a fraction of the time spent on computation of local stiffness matrices.
